\section{Demonstrator Prototype}
\label{sec:prototype}

About 5 pages that gives:

\begin{enumerate}
  
\item High-level view of the demonstrator and its purpose.

\item Details of how the demonstrator has been implemented.

\item May involve presentation of code snippets.

\end{enumerate}

The example below shows how you may include code. There are similar
styles for many other langages - in case you do not use Java in your
project. You can wrap the listing into a figure in case you need to
refer to it. How to create a figure was shown in Section~\ref{sec:background}.
  
\lstinputlisting[language=java]{code/BoksVolum.java}

Borrar encima --------------------------------------------------------------------------------------------------------------------



\subsection{High-Level View}
As any other machine learning project, this prototype learns how to predict the results of new data through the results of a given dataset with the results already set. As a consequence we design a prototype with a big input dataset of 6 Gb to test the technology because implicitly the library prepared for machine learning, the one that we are using, is splitting, parallelizing and clustering when we use the data structure of this library call RDD.\\*

So during that process we are able to test the performance of Apache Spark and its component for machine learning, called MLLib. 
We check the differences in performance using the time spending in every training of a model because it has to compute a big amount of data, as consequence we can test this technology in terms about clustering and parallelizing huge amount of data and compare the results between native clustering and local clustering, by native we mean that we use the component by default with only one core for clustering and by local we mean to use the component with as many core as the machine has (there is a third one call remote clustering that we didn’t achieve to implement so doesn’t make so much sense to talk about that in the report but we did it in the presentation).

\subsection{Implementation}